\documentclass[12pt,A4]{article}


\textheight 9in
\textwidth 6.5in
\oddsidemargin 0.0in
\evensidemargin -0.6in
\topmargin -0.6in
%\linespread{1.5}

\usepackage{amsmath}
%\usepackage{epsfig}
\usepackage{graphics}
%\usepackage{wrapfig}
\usepackage{amssymb}
%\usepackage{multirow}
\usepackage{graphicx}
%\usepackage{comment}
%\usepackage{psfrag}
%\usepackage{listings}
\usepackage{color}
%\usepackage{times}
\newfont{\Bigger}{cmr10 at 2cm}

\newcommand{\qed}{\hfill $\rule{1.7mm}{1.7mm}$}

\newcommand{\eat}[1]{}
\title{\vspace*{-1.5cm} \centerline{ {\Huge{ \bf \hspace{0cm}{\color{blue} R K Engineering Services}}\vspace*{-0.75cm}}}}

\author{\centerline {\color{blue}{39-24-32, Madhavadhara, I E Post, Visakhapatnam - 7}}\\ \\
 \footnotesize {\color{blue}Ref No: RK452013  \hspace*{3cm}   Mobile: +91-9885-861747  \hspace*{3cm} email: prasant@csail.mit.edu}\\
${\color{blue}\rule{7.0in}{0.5mm}}$}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\vspace*{20pt}


{\begin{center}{\bf  \large Profile of RK Engineering Services}\end{center}}

\vspace*{20pt}


\indent {{\em RK Engineering Services} is established in the year 2009 with an objective to assist  Indian industries in Defense Sector. The Company is supported by senior engineers in the field of Mechanical Engineering, Computer Science and Electrical Engineering .} \\

\indent  The principle  activity of the company includes design and analysis of complex machinery for application with complete focus on combat environment. It has very valuable customers who are leading suppliers to the Defense Ministry. The vendors include Kirloskar Pneumatic Compressors, Burcahardt Kompressors, Cummins Engineerings Pvt. Ltd., Tyco Valves, Johnson Controls Pvt. Ltd., Tushaco Pumps Pvt. Ltd. etc. \\
 
 \indent The company has an average turnover of Rs. 30 lacs to 50 lacs over the last four years. The company has established repetition among all leading multinational companies in Defense Sector. The company has also engaged in conducting design and testing for environment condition over the last four years. \\

\indent  It is a proprietorship company, owned by Mr. Prasant Gopal, post graduate in Computer Science and has vast experience in Electrical and Mechanical Engineering. The company is supported by four mechanical/vibration  experts and one CAD-CAM expert for carrying out state  of the art Design \& Analysis. 




\end{document}
