\documentclass[11pt,A4]{article}


\textheight 9in
\textwidth 6.5in
\oddsidemargin 0.0in
\evensidemargin -0.6in
\topmargin -0.6in
%\linespread{1.5}

\usepackage{amsmath}
%\usepackage{epsfig}
\usepackage{graphics}
%\usepackage{wrapfig}
\usepackage{amssymb}
%\usepackage{multirow}
\usepackage{graphicx}
%\usepackage{comment}
%\usepackage{psfrag}
%\usepackage{listings}
\usepackage{color}
%\usepackage{times}
\newfont{\Bigger}{cmr10 at 2cm}

\newcommand{\qed}{\hfill $\rule{1.7mm}{1.7mm}$}

\newcommand{\eat}[1]{}
\title{\vspace*{-1.5cm} \centerline{ {\Huge{ \bf \hspace{0cm}{\color{blue} R K Engineering Services}}\vspace*{-0.75cm}}}}

\author{\centerline {\color{blue}{39-24-18/1, Madhavadhara, I E Post, Visakhapatnam - 7}}\\ \\
 \footnotesize {\color{blue}Ref No: RK452013  \hspace*{3cm}   Mobile: +91-9885-861747  \hspace*{3cm} email: prasant@csail.mit.edu}\\
${\color{blue}\rule{7.0in}{0.5mm}}$}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\vspace*{0.35cm}	
\begin{flushleft}
{
\noindent \begin{tabular}{l}
\noindent To\\
\noindent American Consulate Officer,\\
\noindent The United States Consulate,\\
\noindent Secunderabad, \\
\noindent Andhra Pradesh - 500003.  
\end{tabular}
}
\end{flushleft}
\vspace*{-2cm}
\begin{flushright} May 3, 2013 \end{flushright} 


\vspace*{1cm}
\large{
\noindent 
\noindent Subject:  {\em Visting Boston to attend MIT's Commencement 2013.}\\

\noindent Dear Madam/Sir:\\

I am Prasant Anumanchipalli. I have been a student at 
Massachusetts Institute of Technology (MIT), Cambridge from 
September $2009$ to December $2012$ in the Electrical Engineering 
and Computer Science Department.\\


\noindent During my studies at MIT, I have spawned a start-up by the name RK Engineering Services. We provide  computational solutions to civil engineering and mechanical engineering problems including  simulations to test if the proposed structures can withstand the desired load limits. I have included the tax returns of the firm over the last couple of years with the applicant. Currently, I am working full time on my start-up.

I wish to attend the student graduation ceremony of this prestigious institution on the $6^{th}$ and $7^{th}$
of June 2013. I hold a F1 visa vide {\em control number}  $20\emptyset 9147322\emptyset  \emptyset  01$ issued at Hyderabad post and a B1/B2 visa vide {\em control number} $20\emptyset 9\emptyset 5 \emptyset 7110 \emptyset 04$ issued  by the American Consulate General of Chennai (Madras) post valid till the february of 2019.\\


\noindent On the $8^{th}$ of December 2012, I have exchanged vows with Ms Madhu Surya as per the 
Hindu custom. I would like my spouse to be alongside me at the Commencement. 
I would like you to give us an opportunity to attend the Commencement at this esteemed university.\\

\noindent Thanking you in anticipation.

\vspace*{0.75cm}
\noindent Sincerely,\\\\ \\ 
 \noindent Prasant Anumanchipalli\\
 \noindent Founder \& CEO\\
\noindent {R K Engineering Services } 



\end{document}
