\documentclass[11pt,A4]{article}


\textheight 9in
\textwidth 6.5in
\oddsidemargin 0.0in
\evensidemargin -0.6in
\topmargin -0.6in
%\linespread{1.5}

\usepackage{amsmath}
%\usepackage{epsfig}
\usepackage{graphics}
%\usepackage{wrapfig}
\usepackage{amssymb}
%\usepackage{multirow}
\usepackage{graphicx}
%\usepackage{comment}
%\usepackage{psfrag}
%\usepackage{listings}
\usepackage{color}
%\usepackage{times}
\newfont{\Bigger}{cmr10 at 2cm}

\newcommand{\qed}{\hfill $\rule{1.7mm}{1.7mm}$}

\newcommand{\eat}[1]{}
\title{\vspace*{-1.5cm} \centerline{ {\Huge{ \bf \hspace{0cm}{\color{blue} R K Engineering Services}}\vspace*{-0.75cm}}}}

\author{\centerline {\color{blue}{39-24-32, Madhavadhara, I E Post, Visakhapatnam - 7}}\\ \\
 \footnotesize {\color{blue}Ref No: RK452013  \hspace*{3cm}   Mobile: +91-9885-861747  \hspace*{3cm} email: prasant@csail.mit.edu}\\
${\color{blue}\rule{7.0in}{0.5mm}}$}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{flushleft}
{
\noindent \begin{tabular}{l}
\noindent To,\\
\noindent The Super Intendent,\\
\noindent Central Excise \& Service Tax,\\
\noindent  Division - I, Range-IB,\\
\noindent  Vizag - 500017.  
\end{tabular}
}
\end{flushleft}
\vspace*{-2cm}
\begin{flushright} April 7, 2014 \end{flushright} 


\vspace*{1cm}
\large{
\noindent 
\noindent Subject:  {\sf Payment of service tax regarding}\\

\noindent Dear Madam/Sir:\\

    This has reference to the letter number OC No. 597/2014 dated 28 February, 2014. We have registered for payment of service tax vide service tax number ALDPA3283DST001 during the year 2009 (copy enclosed for reference). During the financial year 2013-14, our financial transactions are as follows (Bank Statement Enclosed). 

\begin{enumerate}
\item \underline {\em From 1 April, 2013 to 30 September, 2013.} \\

\begin{tabular}{|c|c|c|c|c|}
\hline
\ & & & \ & \\
Sl. No. & Vendor Name & \parbox{1.1in}{Transaction Amount ({\bf INR})} &  \parbox{.85in}{ Service Tax Paid({\bf INR)}} & \parbox{1in}{ Receipt No.}\\
\ & & &  & \\
\hline
\ & & &  & \\
1. & \parbox{1.65in}{Tyco Valves \& Controls India Pvt. Ltd.} &  2,30,000 &  28,480 & CK33991468\\
\ & & &  & \\
\hline
\end{tabular}
 \medskip
 \item \underline{\em From 1 October, 2013 to 31 March, 2014.}   {\sf Nil}.
\end{enumerate}


In view of the above, we request to consider and cancel our service tax registration henceforth. We are herewith submitting half-yearly/yearly service tax returns in due course of time.\\

\noindent Thanking you in anticipation.

\vspace*{0.75cm}
\noindent Sincerely,\\\\ \\ 
 \noindent Prasant Anumanchipalli\\
 \noindent Proprietor\\
\noindent {R K Engineering Services } 
\vspace*{-40pt}
\begin{flushright}
\parbox{2in}{{\sf Enclosures} : Service Tax Certificate, Bank Statement \& ST payment receipt.}

\end{flushright}

\end{document}
