\documentclass[11pt,A4]{article}


\textheight 9in
\textwidth 6.5in
\oddsidemargin 0.0in
\evensidemargin -0.6in
\topmargin -0.6in
%\linespread{1.5}

\usepackage{amsmath}
%\usepackage{epsfig}
\usepackage{graphics}
%\usepackage{wrapfig}
\usepackage{amssymb}
%\usepackage{multirow}
\usepackage{graphicx}
%\usepackage{comment}
%\usepackage{psfrag}
%\usepackage{listings}
\usepackage{color}
%\usepackage{times}
\newfont{\Bigger}{cmr10 at 2cm}

\newcommand{\qed}{\hfill $\rule{1.7mm}{1.7mm}$}

\newcommand{\eat}[1]{}
\title{\vspace*{-1.5cm} \centerline{ {\Huge{ \bf \hspace{0cm}{\color{blue} Bhagwan Sri Satya Sai Seva Samiti}}\vspace*{-0.75cm}}}}

\author{\centerline {\color{blue}{39-24-18/1, Murali Nagar, I E Post, Visakhapatnam - 7}}\\ \\
 \footnotesize {\color{blue}Ref No: BH452013  \hspace*{3cm}   Mobile: +91-9490149041  \hspace*{3cm} email: prasant@csail.mit.edu}\\
${\color{blue}\rule{7.0in}{0.5mm}}$}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\vspace*{0.35cm}	
\begin{flushleft}
{
\noindent \begin{tabular}{l}
\noindent To,\\
\noindent Ch. Vasu Prakash,\\
\noindent Sri Prakash VidyaNiketan,\\
\noindent Uplands, Asilmeta,\\
\noindent Visakhapatnam, \\
\noindent Andhra Pradesh.  
\end{tabular}
}
\end{flushleft}
\vspace*{-2cm}
\begin{flushright} September 5, 2014 \end{flushright} 


\vspace*{1cm}
\large{
\noindent 
\noindent Subject:  {\em Request admission for class III orphaned child regarding.}\\

\noindent Dear Sir:\\  \ \\
This unit of seva samiti has adopted Master G. Shanki of III standard. This boy belongs to a fisherman community who are struggling for their livelihood. This bhajan mandal has adopted to give him education and make him a responsible citizen of this great nation. We request you to kindly extend support for this child and support him with boarding and education facility.

We request you to give concession to the boy this academic year as well. We thank you for the help over the last year.\\


\noindent Thanking you in anticipation. We take this opportunity to pray the lord to give your institution  great future.

\vspace*{1.75cm}
\noindent Sincerely,\\\\ \\  \\ 
 \noindent AVS Chari\\
 \noindent Associate Director, NSTL\\
\noindent {Coordinator for Bhajan Mandal.} 



\end{document}
