\documentclass[12pt,A4]{article}


\textheight 9in
\textwidth 6.5in
\oddsidemargin 0.0in
\evensidemargin -0.6in
\topmargin -0.6in
%\linespread{1.5}

\usepackage{amsmath}
%\usepackage{epsfig}
\usepackage{graphics}
%\usepackage{wrapfig}
\usepackage{amssymb}:q
%\usepackage{multirow}
\usepackage{graphicx}
%\usepackage{comment}
%\usepackage{psfrag}
%\usepackage{listings}
\usepackage{color}
%\usepackage{times}
\newfont{\Bigger}{cmr10 at 2cm}

\newcommand{\qed}{\hfill $\rule{1.7mm}{1.7mm}$}

\newcommand{\eat}[1]{}
\title{\vspace*{-1.5cm} \centerline{ {\Huge{ \bf \hspace{0cm}{\color{blue} Gokul Engineering Services}}\vspace*{-0.75cm}}}}

\author{\centerline {\color{blue}{43-9-156/1, R S Mandir, Dondaparty Jn, Visakhapatnam - 16}}\\ \\
 \footnotesize {\color{blue}Ref No: G1985  \hspace*{5cm}   Mobile: +91-9885-861747}\\
${\color{blue}\rule{7.0in}{0.5mm}}$}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\vspace*{20pt}


{\begin{center}{\bf  \large Profile of Gokul Engineering Services}\end{center}}

\vspace*{20pt}


\indent {{\em Gokul Engineering Services} is established in the year 2006 with an objective to assist  Indian industries in Defense Sector. The Company is supported by senior engineers in the field of Mechanical Engineering, Computer Science and Electrical Engineering .} Gokul Engineering Services is a SSI unit engaged in services related to Shock, Noise \& Vibration analysis and development of test specifications and test fixtures for applications on-board Marine vessels.

\indent  The principle  activity of the company includes design and analysis of complex machinery for application with complete focus on combat environment. It has close to 50 valuable customers who are leading suppliers to the Defense Ministry. The vendors include Kirloskar Pneumatic Compressors, Burcahardt Kompressors, Cummins Engineerings Pvt. Ltd., Hindustan Shipyard Ltd., Rodhe \& S Company, Tyco Valves, Tushaco Pumps Pvt. Ltd. \\
 
\noindent It has also carried out a few jobs for M/S Johnson Controls in the past in designing \& conduct of test fixtures for shock tests. Thejob it has carried out include FEM analysis of AC plants, Heat Exchangers, Pumps etc.\\

\noindent The unit is havinga fleet of engineers \& technicians who are dedicated for the work and committed to carry out excellent quality design \& analysis works. It has well experienced advisors and academicians to explore \& advice latest tools/methods towards Design \& Analysis. 



\end{document}
